\Huge \bf \sc Calibration of an inertial measurement unit

### 2013-11-21 latex/icar/paper_sensores/paper.tex
ordenando papers

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{\Huge \bf \sc
Calibration of an inertial measurement unit}

@@

\begin{figure}
	\centering
	\includegraphics[width=.6\columnwidth]{./pics_paper/ejes_acc.jpg}
	\caption{\textbf{Non orthogonality -} Rotations of the sensitivity axis of the accelerometer over the axis of the platform system.}
	\label{fig:nonorto}
\end{figure}

@@

The 27 measures made were the following:
\begin{itemize}
\item Starting position: $x$ axis pointing ``down'': 9 measures were made combining two rotations. First, rotating around the $z$ axis $\theta =0^\circ, 10^\circ, 20^\circ, 30^\circ, 45^\circ$. Then, for each angle defined (except for $\theta = 0^\circ$), two measures were made rotating around the $x$ axis $\psi = 0^\circ, -45^\circ$. This set of measures can be expressed in the following way:
\end{itemize}

@@

\begin{itemize}
\item The typical sensitivity for each axis is $256 bits/g \approx 26.10 bits / m^{s-2}$.
\item The typical offset for each axis is $0 ms^{-2}$.
\item As the axis should be as orthogonal as possible is reasonable to think that the rotation angles $\alpha_{aij}$ are near zero. 
\end{itemize}

@@

It is important to clarify that to perform a perfect temperature compensation, variations of temperatures should be produced with the sensors in different orientations. However, the most important is that the platform is in horizontal position with the $z$ axis pointing ``up''. This is because this particular position is the main operating situation in the application for which this calibration method was thougth.
\section{Results and analysis}
\subsection{Static parameters}
In this section, the parameters that solve problem \ref{eq:calib_problem} are presented for both accelerometer and gyroscope. In addition, the statistic over the test set is studied and analyzed. \\

@@

In Figure \refp{fig:resultado_temp} can be observed that during
the experiment, the uncompensated estimation of g is $9.25ms^{-2}$ instead of
$9.81ms^{-2}$, which means an error of $0.56ms^{-2}$. Such an
error in acceleration measurements can cause severel errors
in applications where the operating temperature can differ
from the calibration temperature, thus, is vital that temperature
compensation is performed.

@@

It was successfully implemented and tested to perform the calibration of the sensors unit (IMU) 
used to estimate the state variables of a quadrotor. Experimental results show a very precise determination of the acceleration and angular velocity. This precision is achieved also during a wide variation of operating temperature of the sensors. This allows satisfactory estimation for flight control in a wide range of operating conditions.

>>>>

\begin{document}
\IEEEoverridecommandlockouts
\IEEEpubid{\makebox[\columnwidth]{978-1-4799-2722-7/13/\$31.00~\copyright~2013 IEEE \hfill} \hspace{\columnsep}\makebox[\columnwidth]{ }}

%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{\Huge \bf \sc
Calibration of an inertial measurement unit}

@@

\begin{figure}
	\centering
	\includegraphics[width=.6\columnwidth]{./pics_paper/ejes_acc_pro.png}
	\caption{\textbf{Non orthogonality -} Rotations of the sensitivity axis of the accelerometer over the axis of the platform system.}
	\label{fig:nonorto}
\end{figure}

@@

We propose 27 measured positions in the following way:
\begin{itemize}
\item Starting position: $x$ axis pointing ``down'': 9 measures were made combining two rotations. First, rotating around the $z$ axis $\theta =0^\circ, 10^\circ, 20^\circ, 30^\circ, 45^\circ$. Then, for each angle defined (except for $\theta = 0^\circ$), two measures were made rotating around the $x$ axis $\psi = 0^\circ, -45^\circ$. This set of measures can be expressed in the following way:
\end{itemize}

@@

\begin{itemize}
\item The typical sensitivity for each axis is $256 bits/g \approx 26.10 bits / ms^{-2}$.
\item The typical offset for each axis is $0 ms^{-2}$.
\item As the axis should be as orthogonal as possible is reasonable to think that the rotation angles $\alpha_{aij}$ are near zero. 
\end{itemize}

@@

It is important to clarify that to perform a perfect temperature compensation, variations of temperatures should be produced with the sensors in different orientations. However, the most important is that the platform is in horizontal position with the $z$ axis pointing ``up''. This is because this particular position is the main operating situation in the application for which this calibration method was thought.
\section{Results and analysis}
\subsection{Static parameters}
In this section, the parameters that solve problem \ref{eq:calib_problem} are presented for both accelerometer and gyroscope. In addition, the statistic over the test set is studied and analyzed. \\

@@

In Figure \refp{fig:resultado_temp} can be observed that during
the experiment, the uncompensated estimation of g is $9.25ms^{-2}$ instead of
$9.81ms^{-2}$, which means an error of $0.56ms^{-2}$. Such an
error in acceleration measurements can cause several errors
in applications where the operating temperature can differ
from the calibration temperature, thus, is vital that temperature
compensation is performed.

@@

It was successfully implemented and tested to perform the calibration of the sensors unit (IMU) 
used to estimate the state variables of a quadrotor. Experimental results show a very precise determination of the acceleration and angular velocity. This precision is achieved also during a wide variation of operating temperature of the sensors. This allows satisfactory estimation for flight control in a wide range of operating conditions. %\cite{0957-0233-18-7-016}
